% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

I would first like to thank my thesis advisor \textbf{Prof. Marcus Liwicki} who was always present physically or virtually whenever I ran into some trouble or had a crazy thought. He consistently steered me in the right the direction whenever he thought I needed it.

I would also like to thank my second thesis advisor \textbf{Felix Laumann} with whom I worked in Copenhagen and in Kaiserslautern. He also made sure Imperial College, London is never far away with our continuous calls and discussion. He assisted in all different work done in the thesis from research to implementation and writing.\\

I would also like to acknowledge \textbf{University of Kaiserlautern} for providing me with the opportunity for writing the thesis and \textbf{MindGarage} for providing me with the computation power.\\

I must express my very profound gratitude to my parents (\textbf{Vivek} and \textbf{Anita}), to my sister (\textbf{Mineshi}) and to \textbf{Purvanshi Mehta} for providing me with unfailing support and continuous encouragement throughout the thesis. 

Finally, I am thankful to \textbf{Ashutosh Mishra}, \textbf{Saurabh Varshneya}, \textbf{Abhash Sinha} and \textbf{Ayushman Dash} for their invaluable comments and endless discussion. I am also thankful to \textbf{Sadique Adnan Siddiqui} for his late night tea and delicious food. This accomplishment would not have been possible without them. \\

I would also like to mention \textbf{BotSupply} for providing me with the funds to go and meet new people to discuss ideas. \\ \\



\end{acknowledgements}
